Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-03 manuscript.Rmd
Minor comments.

```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```

>>>>

```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
# Read data files
# load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
# load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
# hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
# 
# source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
# source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
# 
# combineData.f()
# cleaningJournals.f()
# shortArticles.f()
# titleMatching.f()
# otherDocuments.f()
# fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```
